\wt{173 Weierstrass approximation theorem}
$f: [a,b] \to \R$ cont. then $\forall \epsilon > 0, \exists$ a polynomial $p$ with real coefficients s.t.
$\forall x \in [a,b], |f(x) - p(x)| < \epsilon$.
\wt{174} Let $f: [a,b] \to \R$ be cont. and $\epsilon > 0$.
Then there exists a polynomial $p$ with rational coefficients s.t.
$\forall x \in [a,b], |f(x) - p(x)| < \epsilon$.
\we{175} The set of all polynomials of one variable, of any degree, with rational coefficients is countable.
\wt{176} $C([a,b])$ is separable.
\wt{177} $(X, d)$ metric space $A \subseteq X$, $A \neq \emptyset$, and $d_A$ the induced metric on $A$.
Then the metric space $(A, d_A)$ is separable.
\we{178} The irrationals with the stdmet. on $\R$ are separable.
\wt{} Every compact metric space is separable.
\wt{179 Separable, then second countable} $(X,d)$ a separable metric space, $D \subseteq X$ countable and dense in $X$.
Let $\mathcal{B} = \{B(x,r) : c \in D, r \in \Q^+\}$ be the set of all open balls with rational radius and
center in $D$.
Then $\mathcal{B}$ is countable and every open subset of $X$ is a union of elements of $\mathcal{B}$.
In other words, $\mathcal{B}$ is a countable base for the topology of $X$.
\wde{180 Topological base} $(X, \mathcal{T})$ a topological space, $\mathcal{B} \subseteq \mathcal{T}$.
A base for the topology $\mathcal{T}$ is a family $\mathcal{B}$ of open subsets of $X$ s.t.
every open set in $\mathcal{T}$ is a union of elements of $\mathcal{B}$.
\wde{182 Second countable} A topological space is second countable iff it has a countable base.
\wt{184} In a separable metric space, every family of pairwise disjoint non-empty open sets is countable.
