\wde{81 Topological Space} A topological space is
a set $X$ equipped with a collection $\mathcal{T}$ of subsets of $X$, s.t.
(1) $\emptyset, X \in \mathcal{T}$;
(2) $\mathcal{T}$ is closed under arbitrary unions (closed under means the result of such an operation is in $\mathcal{T}$);
(3) $\mathcal{T}$ is closed under finite intersections.
$\mathcal{T}$ is called a topology on $X$, and the elements of $\mathcal{T}$ are called open sets.
\wde{82 Continuity}
$(X, \mathcal{T}_X)$ and $(Y, \mathcal{T}_Y)$ topological spaces,
$f: X \to Y$ continuous iff the preimage of every open set in $X$ is open in $Y$
$\forall G \in \mathcal{T}_Y, f^{-1}(G) \in \mathcal{T}_X$.
\wde{Homeomorphism} $f$ is a homeomorphism iff
it is a continuous bijection and its inverse is continuous.
If such an $f$ exists, then $X$ and $Y$ are homeomorphic.
Remark: Homeomorphicity preserves topological properties,
e.g. compactness, connectedness, separability, etc.
These are properties that can be defined in terms of open sets.
\we{83} Any function from a discrete metric space to any other metric space is continuous.
\we{84} Any function from any metric space to a discrete metric space is not continuous unless it is constant.
\we{86} Integration on $C([a,b])$ with $d_\infty$ to $\R$ is continuous.
\we{88} Product space $Z = X \times Y$, product metric $D((x,y), (x',y')) = d_X(x,x') + d_Y(y,y')$.
Convergence iff convergence in both $X$ and $Y$.
\we{89} $x, x', y, y' \in X: |d(x,y) - d(x',y')| \leq d(x,x') + d(y,y')$.
\wt{90} $d: X \times X \to \R$ is continuous. (Under the product metric on $X \times X$ and the stdmet. on $\R$.)
\wt{Continuity of Linear Operators}
Matrix multiplication is continuous.
$A$ a matrix with entries in $\R$, $x, x' \in \R^n$.
Then $||Ax||_2 \leq C||x||_2$ for some $C > 0$.
\wt{Metrics over normed linear spaces}
$(X, ||\cdot||_X)$ a normed linear space.
$d: X \times X \to \R$ def. by $d(x,y) = ||x-y||_X$ is a metric on $X$.
\wde{91 Bounded linear operators}
A linear  $T: X \to Y$ is said to be bounded iff
there exists $C > 0$ s.t. $||T(x)||_Y \leq C||x||_X$ for all $x \in X$.
\wt{92 Linear op. continuity} TFAE
(1) T Cont.
(2) T Cont. at $0$.
(3) T Bounded.
\wde{93}
$(X, d_X)$ and $(Y, d_Y)$ metric spaces.
$f: X \to Y$ is Lipschitz iff
$\exists L > 0$ s.t. $d_Y(f(x), f(x')) \leq Ld_X(x,x')$ for all $x, x' \in X$.
If $L < 1$ then $f$ is a contraction.
\wt{94} Lipschitz $\Rightarrow$ UC.
\wde{95 Fixed points}
A fixed point $x \in X$ of $f: X \to X$, where $X \neq \emptyset$ is a point s.t. $f(x) = x$.
